How and Why to run a Hack Week

### 2017-08-21 sections/results.tex
Add a comment that clarifies that we have IRB approval.

We report the outcomes of astro-, geo- and neuro- hack weeks from 2016. In the results from post-workshop surveys, we focus on attitudes towards open science and reproducibility, their own learning outcomes, as well as community building and collaborations.

>>>>

We report the outcomes of astro-, geo- and neuro- hack weeks from 2016. In the results from post-workshop surveys (collected with the approval of the Institutional Review Boards at UW, NYU and UC Berkeley, and with participants' informed consent), we focus on attitudes towards open science and reproducibility, their own learning outcomes, as well as community building and collaborations.
